Somatosensory Response Changes During Illusory Finger Stretching

### 2024-05-28 manuscript.qmd
Update manuscript.qmd with planned analyses

>>>>

## Planned Analyses

*(1 – Positive Control) There will be a greater illusory experience, measured via a subjective illusory experience questionnaire, in the (1a) MS condition compared to the NI condition and in the (1b) MS condition compared to the NIT condition.*

The subjective illusory experience questionnaire was  used as a positive control for the current study. Previous research has shown significantly greater illusion strength for MS conditions compared to non-illusion conditions (Carey et al., 2019; Hansford et al., 2023a), which we attempted to replicate. Questionnaire data were be analysed using R (R Core Team, 2021). A one-way ANOVA (or non-parametric equivalent)would be run to compare the dependent variable of normalised (baseline corrected) illusion score from each independent condition. Given significant findings, post-hoc tests would be run, with Bonferroni correction for 2 comparisons (MS Vs NI, MS Vs NIT) at an initial alpha of 0.05.

Interpretations for hypothesis 1 can be found in the design table (Table 1).

*There will be a significant difference in SSEP response across the electrodes of interest (F1 & FC1) when comparing (2a) the MS condition to the NI condition, when comparing (2b) the UV condition to the NI condition, but (2c) that there will be no significant difference when comparing the NIT condition to the NI condition.*

As mentioned in the EEG pre-processing steps in section 2.4.1, analysis of EEG data involved taking a Fourier transform for each waveform averaged across the electrodes of interest, to obtain the amplitude for each trial at the vibration frequency (26Hz). These amplitudes would then be averaged across trials to give overall results for each participant, before running a repeated measures one way ANOVA (or non-parametric equivalent) comparing SSEP response from each experimental condition. The dependent variable would be SSEP amplitude in µV, whilst the independent variable would be the different manipulations given in each comparison condition. Given significant findings in the ANOVA, post hoc comparisons of every condition would be conducted at a new alpha of .016 (corrected for 3 comparisons (MS Vs NI, MS Vs UV, UV Vs NI)). Based on the pilot data in Appendix A, we expected to see activation most pronounced over mid-frontal distributions, covering F1 and FC1 electrodes and therefore these electrodes were selected as the electrodes of interest.

Interpretations for hypothesis 2 can be found in the design table (Table 1).
